Computing Entropies With Nested Sampling

### 2017-05-27 paper/ms.tex
Updated results

From the algorithm, the expected log-probability was
\begin{align}
\depth_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy was

>>>>

I ran the algorithm and computed the depth using a tolerance of
$L=10^{-3}\sqrt{100}$, so that the RMS difference between
points in the two datasets was about $10^{-3}$.
From the algorithm, the average depth was
\begin{align}
\depth_{\d} &= 698.25 \pm 0.34.
\end{align}
The log-volume of a 100-dimensional ball of radius
$L=10^{-3}\sqrt{100}$ is
$-551.76$. Therefore, the differential entropy is estimated to be
\begin{align}
H_{\d} &\approx 146.49 \pm 0.34.
\end{align}
which is very close to the true value (suspiciously close, but this
was just a fluke).
